ANON paper

### 2014-02-19 paper.tex
Tor design, directory servers subsection

		\subsection{Directory servers}

>>>>

		\subsection{Directory servers}
			The original Onion Router implementation used in-band status updates where each node broadcasts know nodes to its neighbours. An attacker could exploit this to isolate and limit the knowledge of a client, forcing connections through malicious nodes. Beside possible security disadvantages, in-band status updates also have the disadvantage that it takes longer to propagate throughout the network and create a global consensus.

			To mitigate these concerns, Directory Servers were introduced to Tor during its reimplementation to keep a redundant central consensus about the network. They act as HTTP servers to which Tor nodes can publish signed information about themselves. Tor clients can in turn download this information.

			This information is signed by the Directory Servers before it is distributed to the Tor clients. The keys to verify these signatures are preloaded in the Tor software, along with the list of Directory Servers, which implies trust by the Tor client in the Directory Servers.
